Learning Constraints and Optimization Criteria

### 2015-10-23 Paper.tex
Trim and changes in thesis

To avoid extensive coverage ($e \models c$) and entailment ($\sym{T} \models c$) calculations, two additional tests are used.
The subset-test rejects clauses that are supersets of a clause that covers the same or all examples and has been accepted earlier.
Because clauses can be formulated in multiple ways, a representative-test is used to remove clauses that are not in canonical form.
\anton{Not clear, needs more explanation, or should be removed.}

% In the refinement step, clauses are extended to be more general and potentially cover more examples.
% The refinement operator uses a list of atoms that may be added to a clause.
% This list is calculated in advance, given a maximal amount of variables.

@@

The learning process is parameterized by the maximal amount of variables and literals allowed per clause.
If these limits are too large, constraints are found that over-fit the training data.
These constraints are too specific and will exclude valid solutions that are not in the training set.
On the other hand, if the chosen limits are too small, the necessary constraints will not be found.

@@

The moving problem with input according to example~\ref{ex:moving-input} is used to evaluate the learning of optimization criteria.
18 possible configurations are used as available examples~\sym{E}.
Four weighted soft constraints are used to represent the underlying model~\sym{M} for the users preferences.
Two approaches are used for evaluation and differ in the way they construct the training ($\sym{E}_{train}$) and test sets ($\sym{E}_{test}$).
In the first approach, given a parameter~$p_{train}$, the examples~\sym{E} are randomly partitioned into disjoint train and test sets ($\sym{E}_{test}$) such that $\#\sym{E}_{train} = p_{train} \cdot \#\sym{E}$.
The second approach uses $\sym{E}_{train} = \sym{E}_{test} = \sym{E}$.

Preferences are generated by picking two examples $e_1$,~$e_2 \in \sym{E}_{train}$ and ordering them according to their scores $score(e_i, \sym{M})$.
Consider all possible pairwise preferences over $\sym{E}_{train}$: $\mathit{pref}(\sym{E}_{train})$.
Given the fraction $p_{pref}$ of preferences to use, then a random subset~$\sym{P}_{train} \subset \mathit{pref}(\sym{E}_{train})$ of size $p_{pref} \cdot \# \sym{P}$ is used for learning.
Errors in the input preferences are simulated by flipping preferences (e.g. $e_1 \succ e_2$ becomes $e_1 \prec e_2$).
Given the fraction $p_{error}$ of errors to introduce, a random subset $\sym{P}_{error} \cup \sym{P}_{train}$ of the preferences are flipped, where $\#\sym{P}_{error} = p_{error} \cdot \sym{P}_{train}$.

@@

Figure~\ref{fig:fractie} shows how the scores improve as the amount of examples and the fraction of included preferences increases.
In all cases, more than half the pairs of examples are correctly predicted and high scores can be obtained even for small datasets.
Additional experiments have shown that even for lower scores the learned optimization criteria are often capable of identifying the correct optimal solution. \sam{Refer to thesis}

>>>>

@@

The learning process is parameterized by the maximal number of variables and literals allowed per clause.
If these limits are too large, constraints are found that over-fit the training data.
These constraints are too specific and will exclude valid solutions that are not in the training set.
On the other hand, if the chosen limits are too small, the necessary constraints will not be found.

@@

The moving problem with input according to example~\ref{ex:moving-input} is used to evaluate the learning of optimization criteria.
18 possible configurations are used as available examples~(\sym{E}).
Four weighted soft constraints are used to represent the underlying model~(\sym{M}) for the users preferences.
Two approaches are used for evaluation and differ in the way they construct the training ($\sym{E}_{train}$) and test sets ($\sym{E}_{test}$).
In the first approach, given a parameter~$p_{train}$, the examples are randomly partitioned into disjoint train and test sets ($\sym{E}_{test}$), such that $\#\sym{E}_{train} = p_{train} \cdot \#\sym{E}$.
The second approach uses $\sym{E}_{train} = \sym{E}_{test} = \sym{E}$.

Preferences are generated by picking two examples $e_1$,~$e_2 \in \sym{E}_{train}$ and ordering them according to their score: $score(e_i, \sym{M})$.
Consider all possible pairwise preferences over $\sym{E}_{train}$: $\mathit{pref}(\sym{E}_{train})$.
Given the fraction $p_{pref}$ of preferences to use, then a random subset~$\sym{P}_{train} \subset \mathit{pref}(\sym{E}_{train})$ of size $p_{pref} \cdot \# \sym{P}$ is used for learning.
Errors in the input preferences are simulated by flipping preferences (e.g. $e_1 \succ e_2$ becomes $e_1 \prec e_2$).
Given the fraction $p_{error}$ of errors to introduce, a random subset $\sym{P}_{error} \cup \sym{P}_{train}$ of the preferences are flipped, where $\#\sym{P}_{error} = p_{error} \cdot \sym{P}_{train}$.

@@

Figure~\ref{fig:fractie} shows how the scores improve as the number of examples and the fraction of included preferences increases.
In all cases, more than half the pairs of examples are correctly predicted and high scores can be obtained even for small datasets.
Additional experiments have shown that even for lower scores the learned optimization criteria are often capable of identifying the correct optimal solution. \sam{Refer to thesis}
